%% The openany option is here just to remove the blank pages before a new chapter
\documentclass{book}
\usepackage{graphicx}
\usepackage{tcolorbox}
\usepackage{textgreek,url,fancyvrb}
\usepackage{soul}
\usepackage[caption=false]{subfig}
\usepackage[top=1in, bottom=1in, left=1 in, right= 1 in]{geometry}
\usepackage{float}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{csquotes}
\usepackage{url}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage{hyperref}

\renewcommand{\familydefault}{\sfdefault}

\hypersetup{linkcolor=blue, linkbordercolor=0 0 1, colorlinks=true}

\makeatletter
 \def\@textbottom{\vskip \z@ \@plus 1pt}
 \let\@texttop\relax
\makeatother


\setitemize{noitemsep,topsep=1pt,parsep=1pt,partopsep=0pt}
\lstset{
language=C,
numberstyle=\footnotesize,
basicstyle=\ttfamily\footnotesize,
stepnumber=1,
breaklines=true,
showspaces=false,           % Leerzeichen anzeigen ?
showtabs=false,             % Tabs anzeigen ?
frame=L
 }

\newcommand{\specialcell}[2][l]{%
	\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}


\begin{document}

\title{{ ~\\~\\~\\~\\~\\ Data Structures in C \\\Large ~\\Lecture Notes for  CIS*2520 \\~\\University of Guelph\\~\\~\\~\\~\\}}
\author{Judi McCuaig }
\maketitle

\Huge 
Foreward
\\ \\ \\
\normalsize
This document was originally written as supplement to the slides and lectures for CIS*2520.  Recently(early 2017) it has been revised to serve as the main reference document for a distance education version of CIS*2520.   Students using this material are assumed to have  a background in programming in C.   

Special thanks to David McCaughan, Pascal Matsakis and Xining Li for sharing  slides and presentations from their offerings CIS*2520.  D. McCaughan's materials influenced the overall design of the course materials significantly.   Dr. Matsakis and and Dr. Li's work helped greatly to  improve the material on computational complexity,  heaps, and priority queues.


This work is licensed under a Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.


\tableofcontents


\mainmatter




%
\input{intro}
\input{linearstructures}
\input{hashtables}
\input{introtrees}
\input{binarytrees}
\input{heaps}
\input{priorityqueue}
%
%\input{advancedtrees}
\input{complexity}
%\input{sorting}
%\appendix

%\input{questionsolutions}
%\end{appendix}

\end{document}